SAT Solving for Vesicle Traffic Systems in Cells

### 2017-07-20 paper/bio_MTedit.tex
pass

%\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
\label{subsec:graphmodel}
Since a VTS are a transport graph, it is but natural to formally model VTS as graphs (as used in computer science) with their nodes denoting compartments and labeled edges denoting transport vesicles with labels denoting the set of molecules being transported. The pairing mechanism can be represented as matching tables over sets of molecules.
% i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met. 
Given such a graph model of a VTS, then properties, such as $k$-connectedness or stability condition, can be formally defined as constraints, 
%i.e., first-order logical formulas, 
over graphs and function types.  Note that these formulas define among other things constraints over paths between nodes in the graph model of VTS. Similarly, one can define fusion rules as constraints over the boolean functions modeling the regulations.  
% For example, the steady state condition, described informally earlier, can be defined by the formula shown in Listing~1.1.

@@

If a VTS is $k$-connected, every pair of compartments remain reachable after dropping $k-1$ vesicles. In principle the connectivity of a VTS can be determined by cell-biological studies.
% We have previously shown \cite{shukla} that a feasible VTS must be at least 3-connected but might need to have higher connectivity. 
Here we have build a tool that studies properties of VTSs that are not $k$-connected, from some $k$. 
%We later will discuss conditions of maximum connectivity [or LGC, least guarantee connectivity] and minimal connectivity [or LRC, least required connectivity].

>>>>

%\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
\label{subsec:graphmodel}
%
Since a VTS is a transport graph, it is but natural to formally model
VTS as graphs (as used in computer science) with their nodes denoting
compartments and labeled edges denoting transport vesicles with labels
denoting the set of molecules being transported. The pairing mechanism
can be represented as matching tables over sets of molecules.
% i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met. 
%
Given such a graph model of VTSs and their properties, such as
stability condition and fusion rules, can be formally defined as
constraints over graphs and uninterpreted Boolean functions.
%
% Note that the formulas define among other things constraints over
% paths between nodes in the graph model of VTS. Similarly, one can
% define fusion rules as constraints over the boolean functions modeling
% the regulations.  
\
% For example, the steady state condition, described informally earlier, can be defined by the formula shown in Listing~1.1.

@@

If a VTS is $k$-connected, every pair of compartments remain reachable after dropping $k-1$ vesicles. In principle the connectivity of a VTS can be determined by cell-biological studies.
\ankit{Why $k$-connected matters?}
% We have previously shown \cite{shukla} that a feasible VTS must be at least 3-connected but might need to have higher connectivity. 
Here we have build a tool that studies properties of VTSs that are not $k$-connected, from some $k$. 
%We later will discuss conditions of maximum connectivity [or LGC, least guarantee connectivity] and minimal connectivity [or LRC, least required connectivity].
